---
title: "GWAS pairwise colocalization"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
---
```{r include = FALSE}
library(vroom)

traits_v <- if (!is.null(params$traits_ordered) && nzchar(as.character(params$traits_ordered))) {
  unlist(strsplit(as.character(params$traits_ordered), "|", fixed = TRUE))
} else {
  character()
}
ancestries_v <- if (!is.null(params$ancestries_ordered) && nzchar(as.character(params$ancestries_ordered))) {
  unlist(strsplit(as.character(params$ancestries_ordered), "|", fixed = TRUE))
} else {
  character()
}

if (length(traits_v) != length(ancestries_v)) {
  traits_v <- character()
  ancestries_v <- character()
}

anc_trim <- ancestries_v[nchar(trimws(ancestries_v)) > 0L]
uniq_anc <- sort(unique(trimws(anc_trim)))
cross_ancestry <- length(uniq_anc) > 1L

coloc_exist <- nzchar(as.character(params$coloc_results)) && file.exists(as.character(params$coloc_results))
coloc_tbl <- if (coloc_exist) {
  suppressWarnings(vroom::vroom(as.character(params$coloc_results), show_col_types = FALSE))
} else {
  NULL
}
```

```{r echo = FALSE}
if (length(traits_v) > 0L && identical(length(traits_v), length(ancestries_v))) {
  kv <- data.frame(trait_prefix = traits_v, ancestry = ancestries_v, stringsAsFactors = FALSE)
  knitr::kable(kv, caption = "Input GWAS (standardised → clumped → finemapped)")
}
```

### Colocalization priors & overlap

Overlapping finemapped signals were defined within ± **`r params$overlap_kb`** kb (pairs of credible-set leads on the same chromosome with lead positions within this window).

| Setting | Value |
|---------|-------|
| `overlap_kb` | `r params$overlap_kb` |
| `p1` | `r params$p1` |
| `p2` | `r params$p2` |
| `p12` | `r params$p12` |

```{r echo = FALSE, results = 'asis'}
if (cross_ancestry) {
  ld_phrase <- if (length(uniq_anc) == 2L) {
    paste0("between ", uniq_anc[1], " and ", uniq_anc[2])
  } else {
    paste0("among the populations (", paste(uniq_anc, collapse = ", "), ")")
  }
  cat(paste0(
    "> **Cross-ancestry colocalization detected.**\n>\n>",
    "> Differences in LD structure ", ld_phrase,
    " can **result in false-negative colocalization signals** (**H3**; incompatible ",
    "causal variants in the region — see PP.H3.abf vs PP.H4.abf in the `coloc` output).\n>\n>",
    "> Fine-mapping / LD reference ancestries used in this run: **",
    paste(ancestries_v, collapse = "**, **"),
    "**.\n"
  ))
}
```

```{r echo = FALSE, results = 'asis'}
if (!cross_ancestry && length(uniq_anc) == 1L) {
  cat(paste0(
    '*All GWAS in this pipeline were analysed with ancestry **',
    uniq_anc[1],
    '** for LD (clumping / fine-mapping).*\n\n'
  ))
}
```


### Colocalization results

Overlapping signals were tested pairwise with `coloc::coloc.bf_bf()` using SuSiE-derived log-Bayes-factor columns from the fine-mapping outputs.

```{r echo = FALSE}
if (!is.null(coloc_tbl) && nrow(coloc_tbl) > 0L) {
  knitr::kable(dplyr::arrange(coloc_tbl, dplyr::desc(PP.H4.abf)) |> dplyr::filter(PP.H4.abf > 0.8), caption = "All significant (PP.H4.abf > 0.8) pairwise colocalisation results")
} else {
  cat("(No significant pairwise colocalisation rows returned — insufficient overlapping finemap signals across traits.)")
}
```

### Additional info

**Please do us a favour and cite this pipeline: https://doi.org/10.5281/zenodo.10624713**

* This pipeline was run using the github repository: https://github.com/MRCIEU/GeneHackman
* and the docker image: docker://mrcieu/genehackman:`r get_docker_image_tag()`
* `coloc` R package: https://doi.org/10.1371/journal.pgen.1004383
* `coloc` guide: https://chr1swallace.github.io/coloc/
