---
title: "GWAS Comparison Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
---
```{r include = F}
library(vroom)
library(dplyr, quietly=T)
```

### Plots Comparing Heterogeneity Across Significant SNPs

`r sprintf("![Plot comparing the heritability across clumped SNPs](%s)", params$heterogeneity_plot)`
`r sprintf("![Forest Plot Comparing clumped SNPs that fail heterogeniety score](%s)", params$heterogeneity_snp_comparison)`

### Expected vs Observed Results

This shows all expected vs. observed results run across all GWAS
```{r echo=F}
expected_vs_observed <- vroom::vroom(params$results, show_col_types = F)
knitr::kable(expected_vs_observed)
```
### Table of Heterogeneity Results


```{r echo=F}
heterogeneity_results <- vroom::vroom(params$heterogeneity_scores, show_col_types = F)
knitr::kable(heterogeneity_results)
```
### References
* Expected vs Observed doi: 10.1038/nature17671

### Additional info

* This pipeline was run using the github repository: https://github.com/MRCIEU/gwaspipeline
* and the docker image: docker://mrcieu/gwaspipeline:`r get_other_docker_tag()`
