---
title: "GWAS Comparison Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
---

### LDSC Result Files


```{r echo = F}
ldsc_result_files <- Sys.glob(paste0(params$ldsc_directory, "*"))
for (file in ldsc_result_files) {
  cat(paste0("\n\n", file, "\n\n"))
  base::readLines(file) |> paste0(collapse = "\n") |> cat()
}

```

### Plots Comparing Heterogeneity Across Significant SNPs

`r sprintf("![Plot comparing the heritability across clumped SNPs](%s)", params$heterogeneity_plot)`
`r sprintf("![Forest Plot Comparing clumped SNPs that fail heterogeniety score](%s)", params$heterogeneity_snp_comparison)`

### Expected vs Observed Results

This shows all expected vs. observed results run across all GWAS
```{r echo=F}
expected_vs_observed <- vroom::vroom(params$results, show_col_types = F)
knitr::kable(expected_vs_observed)
```
### Table of Heterogeneity Results


```{r echo=F}
heterogeneity_results <- vroom::vroom(params$heterogeneity_scores, show_col_types = F)
knitr::kable(heterogeneity_results)
```
### References
* Expected vs Observed doi: 10.1038/nature17671
* LDSC: https://github.com/bulik/ldsc?tab=readme-ov-file#citation

### Additional info

**Please do us a favour and cite this pipeline: https://doi.org/10.5281/zenodo.10624713**

* This pipeline was run using the github repository: https://github.com/MRCIEU/GeneHackman
* and the docker image: docker://mrcieu/genehackman:`r get_docker_image_tag()`
