---
title: "GWAS Comparison Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
---

### LDSC Result Files

LD Score Regression (LDSC) estimates SNP heritability (h²) and genetic correlation (rg) between each pair of GWAS; each file below corresponds to one ancestry group.

```{r echo = F}
ldsc_result_files <- Sys.glob(paste0(params$ldsc_directory, "*"))
for (file in ldsc_result_files) {
  cat(paste0("\n\n", file, "\n\n"))
  base::readLines(file) |> paste0(collapse = "\n") |> cat()
}

```

### Plots Comparing Heterogeneity Across Significant SNPs

The first plot shows the per-GWAS contribution to the Cochran's Q heterogeneity statistic for **all** clumped SNPs (one row per SNP). The second plot is a grouped forest plot of effect sizes for the **subset** of SNPs whose heterogeneity Q p-value passes Bonferroni correction (Q p-value < 0.05 / number of SNPs tested), i.e. only the significantly heterogeneous SNPs.

`r sprintf("![Per-GWAS contribution to heterogeneity Q-statistic (all clumped SNPs)](%s)", params$heterogeneity_plot)`
`r sprintf("![Forest plot of effect sizes for SNPs with significant heterogeneity (Bonferroni-corrected)](%s)", params$heterogeneity_snp_comparison)`

### Expected vs Observed Results

Compares the expected replication rate (based on discovery effect sizes and replication standard errors) against the observed replication rate across all GWAS pairs — a discrepancy suggests winner's curse or population differences.

```{r echo=F}
expected_vs_observed <- vroom::vroom(params$results, show_col_types = F)
knitr::kable(expected_vs_observed)
```
### Table of Heterogeneity Results

Per-SNP Cochran's Q p-values and per-GWAS contribution p-values (Qj) for all clumped SNPs tested for heterogeneity of effect sizes across the input GWAS.

```{r echo=F}
heterogeneity_results <- vroom::vroom(params$heterogeneity_scores, show_col_types = F)
knitr::kable(heterogeneity_results)
```
### References
* Expected vs Observed doi: 10.1038/nature17671
* LDSC: https://github.com/bulik/ldsc?tab=readme-ov-file#citation

### Additional info

**Please do us a favour and cite this pipeline: https://doi.org/10.5281/zenodo.10624713**

* This pipeline was run using the github repository: https://github.com/MRCIEU/GeneHackman
* and the docker image: docker://mrcieu/genehackman:`r get_docker_image_tag()`
