---
title: "Disease Progression Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
---
```{r include = F}
library(vroom)
library(dplyr, quietly=T)
```

### Unadjusted Manhattan Plots of GWAS
`r sprintf("![Miami Plot Comparing Unadjusted GWAS at p = 0.0001](%s)", params$unadjuested_miami_plot)`

### Comparison of Collider Bias Results
```{r echo=F}
collider_bias_results <- vroom::vroom(params$collider_bias_results, show_col_types = F)
knitr::kable(collider_bias_results)
```

### Expected vs Observed Results

This shows all expected vs. observed results when comparing the incident vs. subsequent GWASes
```{r echo=F}
expected_vs_observed <- vroom::vroom(params$expected_vs_observed, show_col_types = F)
knitr::kable(expected_vs_observed)
```

### Adjusted Manhattan Plots of GWAS
`r sprintf("![Miami Plot of SlopeHunter Adjusted GWAS at p = 0.0001](%s)", params$slopehunter_adjusted_miami_plot)`

### Comparing GWAS Results Across Top Hits in Subsequent GWAS

This is a comparison of all top hits returned from clumped subsequent unadjusted
```{r echo=F}
clumped_snps <- data.table::fread(params$clumped_subsequent)$SNP
columns <- c("SNP", "RSID", "BETA", "SE", "P")

subsequent <- vroom::vroom(params$subsequent_gwas, show_col_types = F) |>
        subset(RSID %in% clumped_snps, select = columns)
subsequent$GWAS <- "Subsequent"

incidence <- vroom::vroom(params$incidence_gwas, show_col_types = F) |>
  subset(RSID %in% subsequent$RSID, select = columns)
incidence$GWAS <- "Incidence"

subsequent_adjusted <- vroom::vroom(params$slopehunter_results, show_col_types = F) |>
  subset(RSID %in% subsequent$RSID, select = columns)
subsequent_adjusted$GWAS <- "Subsequent Adjusted"

all_clumped <- rbind(incidence, subsequent, subsequent_adjusted) |>
  arrange(SNP) |>
  select(GWAS, SNP, everything())

knitr::kable(all_clumped)
```
### Alternative collider bias corrections

If you want to correct the original subsequent gwas (`r params$subsequent_gwas`) using different BETA and SE as calculated in collider bias results section above, please run this command inside a `sbatch` script
```
module add apps/singularity/3.8.3
singularity run -B /user/work/$(whoami) -B /user/home/$(whoami) --pwd /home/scripts/ \
    docker://mrcieu/genehackman:latest \
    adjust_gwas_for_collider_bias.R --gwas <SUBSEQUENT_GWAS> \
        --harmonised_effects_gwas <HARMONISED_GWAS> \
        --beta <BETA> \
        --se <SE> \
        --output_gwas <OUTPUT_FILE_NAME>
```

### Additional info

* This pipeline was run using the github repository: https://github.com/MRCIEU/GeneHackman
* and the docker image: docker://mrcieu/genehackman:`r get_docker_image_tag()`
