---
title: "MR for `r params$dataset` QTL Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
---
```{r include = F}
library(vroom)
library(dplyr, quietly=T)
coloc_results <- vroom::vroom(params$coloc_results, show_col_types = F)
options(scipen=1)
```

### Volcano Plot of MR Results Against `r params$dataset` QTL Dataset
`r sprintf("![](%s)", params$volcano_plot)`

### Statistically Significant MR results (after FDR correction)
Only showing top 20 results if there are more.
```{r echo=F}
mr_results <- vroom::vroom(params$mr_results, show_col_types = F) |>
  subset(p.adjusted < 0.05 & EXPOSURE %in% coloc_results$exposure) |>
  dplyr::arrange(p.adjusted) |> select(-c(id.exposure, id.outcome))

knitr::kable(head(mr_results, 20))
```

### Coloc Results
```{r echo=F}
coloc_results <- coloc_results |> dplyr::filter(exposure %in% mr_results$EXPOSURE)
knitr::kable(coloc_results)
```

### Additional info

**Please do us a favour and cite this pipeline:: https://doi.org/10.5281/zenodo.10624713**

This pipeline was run using the github repository: https://github.com/MRCIEU/GeneHackman
and the docker image: docker://mrcieu/genehackman:`r get_docker_image_tag()`
